Survivable Set Connectivity

### 2015-05-13 draft.tex
small changes in intro

\begin{quote}
\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
\end{quote}

@@

At this time, it seems that Survivable Set Connectivity is only interesting from a theoretical standpoint, as a ``natural" generalization of Set Connectivity. It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.

>>>>

\begin{quote}
\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
\end{quote}

@@

At this time, it seems that Survivable Set Connectivity is motivated primarily by theoreitcal interest, as a ``natural" generalization of Set Connectivity. It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.
